Cryptographic assurance of secrecy and fairness in voting

### 2012-12-07 paper/paper.tex

Essentially, both \term{Scantegrity} and \term{Helios} use some mechanism to shuffle votes so that -- even
with votes decrypted for tallying -- encrypted ballots cannot be linked to their plaintext
counterparts.

@@

Where Table R lies between encryptions and decryptions in \term{Scantegrity}, \term{Helios} makes use of a
cryptographic \term{mixnet} -- performed with cast ballots in hand -- to prevent an attacker from
tracing a vote to its decryption. Unlike in \term{Scantegrity}, \emph{all} encrypted votes can be traced to
their mixnet input, and \emph{all} mixnet outputs can be traced to a location in the tally; however,
those one cannot connect those two traces, such that secrecy is preserved.

@@

At the time a ballot is cast, both \term{Scantegrity} and \term{Helios} attempt to ensure a voter that her
vote is recorded exactly as intended.

@@

\term{Helios} does not actually permit a voter to verify the ballot that she actually casts. Rather, it
allows users to verify a ballot without casting it (after which point it cannot be cast without
a new encryption). The assumption here is that \emph{some} voter will choose to audit a ballot, and
so the system cannot simply cheat and show the user a predetermined hash: it \emph{must} be a valid
one -- otherwise the deception would be revealed should the voter choose to exercise her right
to audit.

>>>>

Essentially, each of these system uses some mechanism to ``shuffle'' votes so that -- even
with votes decrypted for tallying -- encrypted ballots cannot be linked to their plaintext
counterparts.

@@

Where Table R lies between encryptions and decryptions in \term{Scantegrity}, \pv\ and \term{Helios} makes use of a
cryptographic \term{mixnet} -- performed with cast ballots in hand -- to prevent an attacker from
tracing a vote to its decryption. Unlike in \term{Scantegrity}, \emph{all} encrypted votes can be traced to
their mixnet input, and \emph{all} mixnet outputs can be traced to a location in the tally; however,
those one cannot connect those two traces, such that secrecy is preserved.

@@

At the time a ballot is cast, these systems attempt to ensure a voter that her
vote is recorded exactly as intended.

@@

\pv\ provides each voter with multiple ballots, one of which she actually casts, and the others
she can audit to verify that the candidate permutation on the left-hand side corresponds to the one
encoded in the onion on the right-hand side. Audited ballots cannot be cast, but since she chooses
her actual ballot at random, if her audited ballots verify, she gains some confidence that
her real ballot would as well. Auditing authorities also verify randomly selected ballots before,
during, and after polling to garner further assurance.

Like \pv, \term{Helios} does not actually permit a voter to verify the ballot that she actually casts. Rather, it
allows users to verify a ballot without casting it (after which point it cannot be cast without
a new encryption). The assumption here is that \emph{some} voter will choose to audit a ballot, and
so the system cannot simply cheat and show the user a predetermined hash: it \emph{must} be a valid
one -- otherwise the deception would be revealed should the voter choose to exercise her right
to audit.
